---
title: "Portfolio 4 MAP test- Thesis study 1"
author: "Adam Paul"
date: "3/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> The purpose of this portfolio is to run the analyses for study 1 of my thesis. It is based on the analyses set up in Portfolio 4 (yes, the numbering is odd to me too).

## Set-up

The main packages I need are lavaan and lmertest, but semPlot is used to create a visual model. The rest of the libraries are to ensure I have the other programs I may need.


library('psych')
library('reshape2')
library('dplyr')
library('lavaan')
library('Rcpp')
library('lme4')
library('lmerTest')
library('OpenMx')
library('semPlot')
library('tidyverse')
rm(list=ls())

##### Bringing in the data

Data downloaded from Qualtrics as a .csv

```{r bringing in data}
study1 <- read.csv("~/Master's Program Wake Forest/Research/Online Belonging/Thesis Study 1/Online Course Experiences (Excel cleaned).csv", row.names=NULL, stringsAsFactors=TRUE)
View(study1)
```

Ensuring the dataframe is a tibble (be proud, Mason)

as_tibble(study1)

## Data cleaning

Will need to create composite variable for prompted disclosure out of two items.

##### Basic data cleaning

Changing the name of the variable for time spent on the survey. Several variable names were changed in excel. Specifically, the names of the gender responses were changed from a number to their actual gender identity (e.g., demog_gender_1 became demog_gender_female)

names(study1)[6] <- 'duration_seconds'


### Checking for bad data

Checking for bad actors in the data, before giving credit.

summary(study1$duration_seconds)

```{r Filtering}
#looking narrowly at people under the 1st quartile (172)

filter(study1, duration_seconds < 172) %>%
        arrange(duration_seconds)
```

I found no straight-lining within this subset, which suggests to me that the data was all given in good faith. However, I wanted to look at another subset.

I filtered for students that answered positively on two items that previous research suggest should be opposite, belonging and feeling like an outsider.

```{r}
filter(study1, school_belong > 4, school_outsider > 4)
#40 students fall into this category

filter(study1, class_belong > 4, class_outsider > 4)
#18 students fall into class.

filter(study1, school_belong > 4, school_outsider > 4, class_belong > 4, class_outsider > 4)
#4 students fall into this category. Only one seemed suspicious, but passed along to Shannon to make a decision.

```

Removing identifying information from the dataset.

```{r}
study1 <- subset(study1, select= -c(StartDate, EndDate, Status,	IPAddress, Progress,
                Finished, RecordedDate, ResponseId, RecipientLastName, RecipientFirstName,
                RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude,
                DistributionChannel, UserLanguage))

```


### Descriptives cleaning

##### Gender dummy coding

The names of the gender variables have been changed, but I do need to look at them more closely to dummy-code them.

```{r checking gender demographics}
study1 %>%
        filter(is.na(demog_gender_female), is.na(demog_gender_male)) %>%
        count(demog_gender_trans, demog_gender_twospirit, demog_gender_genderqueer, demog_gender_other, demog_gender_no_answer)

study1 %>%
count(demog_gender_trans, demog_gender_twospirit, demog_gender_genderqueer, demog_gender_other, demog_gender_no_answer)

```

We have 12 people that did not identify as either male or female in some way. Due to this small number, there is not much we can do with these individual's gender, so I am going to make two variables, gender_male & gender_nonbinary.



```{r making gender dummy code}
study1 %>%
        mutate(demog_gender_nonbin = 
                       case_when(demog_gender_trans == 1 & demog_gender_female == NA & demog_gender_male == NA ~ 1, 
                                 demog_gender_female == 1 ~ 0,
                                 demog_gender_male ==1 ~ 0,
                                 )) %>%
        select(demog_gender_nonbin, demog_gender_trans)
```

```{r}
study1 %>%
        mutate(V5 = case_when(demog_gender_female == 1 | demog_gender_male == 1 ~ 0
                              
                              )) %>%
        select(V5, demog_gender_female) %>%
        arrange(V5)
```

```{r}
test1 <- study1 %>%
        mutate(demog_gender_nonbin = case_when(is.na(demog_gender_female) & is.na(demog_gender_male) ~ 1 ))



test1 %>%
        select(demog_gender_nonbin, demog_gender_female, demog_gender_male, demog_gender_trans) %>%
        arrange(desc(demog_gender_trans))

```


WHY IS THIS SO FUCKING HARD??????

```{r}
test1 <- study1 %>%
        mutate(demog_gender_nonbin = case_when(demog_gender_trans == 1 | demog_gender_twospirit == 1 | demog_gender_genderqueer == 1 | demog_gender_other == 1 | demog_gender_no_answer == 1 & is.na(demog_gender_female) & is.na(demog_gender_male) ~ 1 ))



test1 %>%
        select(demog_gender_nonbin, demog_gender_female, demog_gender_male, demog_gender_genderqueer, demog_gender_trans) %>%
        arrange(desc(demog_gender_genderqueer))



```

```{r}
study1 %>%
        mutate(demog_gender_nonbin = ifelse(!is.na(demog_gender_female), 0, 1 & demog_gender_trans == 1)) %>%
                       select(demog_gender_nonbin, demog_gender_female, demog_gender_trans) %>%
        arrange(desc(demog_gender_trans))
```

```{r}
study1 %>%
        mutate(demog_gender_nonbin = ifelse(!is.na(demog_gender_female) & !is.na(demog_gender_male), 0, 1)) %>%
                       select(demog_gender_nonbin, demog_gender_female, demog_gender_trans) %>%
        arrange(desc(demog_gender_trans))
```




select(demog_gender_dich, demog_gender_male, demog_gender_female)


study1 <- study1 %>%
        mutate(demog_gender_dich = demog_gender_female == 1) 

##### Race dummy coding



### Variables of Interest

##### Institutional belonging (belong_instit_comp4)


##### Class belonging (belong_class_comp4)


##### Class disclosure (cdiscl_disclose_comp3)


##### Class prompted disclosure (cdiscl__prompt_comp2)


#### Group disclosure (gdiscl_disclose_comp3)


##### Group prompted disclosure (gdiscl_prompt_comp2)



If I decide it's necessary, I will rename variables to make the models easy to think about here.

------------------

# MEDIATION MODELS

------------------

> This section is information given to me by Shannon, kept here and in other path analysis portfolios so I have access to them.

Reminder: Rules of thumb to evaluate goodness of fit: CFI/TLI > 0.95, RMSEA < 0.05, SRMR < 0.06  (Reference: Hu & Bentler, 1999)

### References: 
> http://davidakenny.net/cm/fit.htm
 https://www.psychologie.uzh.ch/dam/jcr:ffffffff-b371-2797-0000-00000fda8f29/chisquare_diff_en.pdf
 Chi-Square Distribution Table: http://sites.stat.psu.edu/~mga/401/tables/Chi-square-table.pdf
 http://www.structuralequations.com/resources/Basic_lavaan_Syntax_Guide_Aug1_2013.pdf

------------------

# Current settings 

------------------

### Resampling 
 Right now, bootstraps are set at 1000 resamples. This to make running the script not take impossibly long
 When running final models, 10000 resamples would probably be preferred - but it'll take a while. 

### Type of CIs
 lavaan can handle four types of bootstrapped CIs; add "boot.ci.type = " to parameterEstimates
 options for types are "norm", "basic", "perc" (percentile), and "bca.simple" 
 defualt is "perc" (I think )

### Significance Levels
 alpha level for bootstrapping can be adjusted; add "level = " to parameterEstimates 
 options for levels are e.g., "95", "99"

------------------

## Model time!

------------------

##### Hypotheses

H1: Students who disclose in a class or small group will report higher feelings of belonging in the class and at their institution.

H2: Prompting disclosure in class or in small groups will be associated with greater disclosure and greater sense of belonging at the classroom and institutional level, as well as whether the relationship between disclosure and institutional belonging is mediated by classroom belonging.

>These are the covariates I am including in the model:
Gender, with female as the reference class: 
        gender_identity_dich 
Race, with white as the reference class: 
        race_asian race_black race_hispanic race_multiracial 
Classmates and group members known prior:
        classmates_know groupdesc_know_prior

#### Creating the model!

```{r Model creation}

```

```{r old model creation}
model_1 <-   '  #Class Belonging direct effects
                belong_class_comp4 ~ a*cdiscl_disclose + gender_identity_dich + race_asian 
                + race_black + race_hispanic + race_multiracial + classmates_know +                          groupdesc_know_prior
                
                belong_class_comp4 ~ b*gdiscl_disclose
                
                #WFU Belonging direct effects
                belong_wfu_comp4 ~ c*cdiscl_disclose + gender_identity_dich + race_asian 
                + race_black + race_hispanic + race_multiracial + classmates_know +                          groupdesc_know_prior
                
                belong_wfu_comp4 ~ d*gdiscl_disclose
                
                #Mediator for class disclosure
                cdiscl_disclose ~ e*cdiscl_prompt_discl
                belong_class_comp4 ~ cdiscl_prompt_discl
                belong_wfu_comp4 ~ cdiscl_prompt_discl
                
                #Mediator for group disclosure
                gdiscl_disclose ~ f*gdiscl_do_emot
                belong_class_comp4 ~ gdiscl_do_emot
                belong_wfu_comp4 ~ gdiscl_do_emot
                
                #removing correlation between prompted disclosures
                cdiscl_prompt_discl ~~ 0*gdiscl_do_emot 
                '
```

#### Testing the fit


```{r testing fit}
fit <- sem(model_1, data=Classroom_Experiences)

summary(fit, fit.measures=TRUE, standardize=TRUE, rsquare=TRUE)
```

#### Graphing!

> Will need to import graph from whichever markdown gets it right. 

```{r Path visualization}
semPaths(fit, whatLabels="par", layout="tree", nCharNodes=0, sizeMan=12, sizeMan2=6)
```

#### Bootstrapping

#####for boot strapped 95% CIs

```{r bootstrapped code}
fit <- sem(model_1, data=Classroom_Experiences, se="bootstrap", bootstrap = 10000)
summary(fit, fit.measures=TRUE, standardize=TRUE, rsquare=TRUE)
```

# What does the data mean?

>This section will be used for me to write up what I've learned from the data analysis, as a point to reference the findings while I'm working later.

>H1: Students who disclose in a class or small group will report higher feelings of belonging in the class and at their institution.

XXXXXXXXXXXXXXXXXXXXXXXX

>H2: Prompting disclosure in class or in small groups will be associated with greater disclosure and greater sense of belonging at the classroom and institutional level, as well as whether the relationship between disclosure and institutional belonging is mediated by classroom belonging.

XXXXXXXXXXXXXXXXXXXXXXXX